A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-09-11 docs/results_JAMwithNFW_v1.01.tex
Removed some TO DOs.

\paragraph{Including a NFW halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone. A dark matter halo in addition to the stellar component could explain these findings. We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} times a constant stellar mass-to-light ratio $\Upsilon_*$), and b) a spherical NFW dark matter component \citep{Navarro+1995c,NFW96}. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile
\begin{equation*}
\rho_\text{NFW}(r) \propto 1 / \frac{r}{R_\text{s,NFW}} \left( 1 + \frac{r}{R_\text{s,NFW}} \right)^2.
\end{equation*}
The NFW halo has two free parameters, the scale length $R_\text{s,NFW}$ and a parameter describing the total mass of the halo. We use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological [TO DO: how to express this] critical density, i.e.
\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by $c_{200}\equiv r_{200} / R_{s,NFW}$. [TO DO: so toll ist das mit der Radiusbenennung noch nicht.????]. There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology \citep{WMAP5cosm} to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their table A2).

\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta)$ [TO DO: $\beta$ or $\beta_0$???] [TO DO: Einheitlich $\Upsilon_{I,*}$????], where $\beta$ is the constant velocity anisotropy parameter (see \S\ref{sec:model_JAM}). We will investigate this parameter space with a MCMC \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
\\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
\begin{equation*}
y = y_0 \left( \frac{x}{x_0} \right)^\alpha \left[ \frac 12 + \frac 12 \left(\frac{x}{x_0} \right)^\gamma \right]^{(\beta - \alpha)/\gamma},
\end{equation*}
where $x= m_*$ [$M_\odot h^{-2}$] is the stellar mass, $y = \frac{\langle M_{200}\rangle}{m_*}$ and $\langle M_{200}\rangle$ [$M_\odot h^{-2}$] is the mean halo mass. The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ \citet{Dutton10}. Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate [TO DO: introduce somewhere], we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation*}
p(v_{200}) = \mathscr{N}(200 \text{km/s} ,40 \text{km/s}).
\end{equation*}
\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Eq. (\ref{eq:Maccio08}) as a prior on the concentration, i.e.
\begin{equation*}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
\end{equation*}
\\For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
\begin{equation*}
p(\beta) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta) \\
&&= \frac{1}{\ln\left( 10 R_{s,NFW}\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 R_{s,NFW}\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},R_{s,NFW})$.
\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec  [TO DO: make sure R' everywhere ???]. We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit. [TO DO: Didn't include the results from the Moster 2010 relation, because they where quite close to the Dutton 2010 relation anyway. Or should I?]

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $R_\text{s,NFW}$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200 \text{km/s},40 \text{km/s})$ (green) and the concentration vs. halo mass relation by \citet{Maccio08} from Eq. (\ref{eq:Maccio08}) in terms of $v_{200}$ vs. $R_\text{s,NFW}$ with $1\sigma$ scatter (blue). The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse). The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}.}
\label{fig:modelB4_triangle}
\end{figure*}

@@

\begin{figure*}
\centering
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Circular velocity curve.}
  \label{fig:modelB4_vcirc}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:F814WMGE}) and dark matter (grey). \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.[TO DO: radius benennungen sind irgendwie verrutscht]}
\label{fig:modelB4_models}
\end{figure*}

\paragraph{Rotation curve.} Following the procedure in \S\ref{sec:model_JAM} we find the rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit} by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5$ arcsec. The best fit with $\kappa' = 0.76$ is shown in the second panel of Figure \ref{fig:modelB4_vrot}. The third panel gives the dispersion that was calculated simply by $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core. Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii fits the data also very well. While the dispersion $\sigma$ in the center fits by construction quite good, there is a huge discrepancy at large radii. The predicted dispersion is much larger than the data; we would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200 km/s$ are more likely to be observed in the pressure supported bulges of galaxies. There \emph{might} be something unexpeted with the $\sigma$ measurements around $\sim 5$ arcsec, but at large radii the the best fit model NFW halo is simply too massive.

\begin{figure*}
\centering
\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Eq. (\ref{eq:kappa_profile}) (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure [TO DO: REF FIGURE] as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also greatly predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
\label{fig:modelB4_vrot}
\end{figure*}

>>>>

\paragraph{Including a NFW halo.} The dynamical modelling attempts in the previous sections suggest that J1331's inner regions have a slightly more roundish and at large radii more massive mass distribution than expected from the distribution of stars alone. A dark matter halo in addition to the stellar component could explain these findings. We therefore proceed by modelling the mass distribution with a) a stellar component, which we get from the light MGE in Table \ref{tab:MGEF814W} (deprojected to the intrinsic $\nu(R,z)$) times a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$), and b) a spherical NFW [TO DO: introduce abbreviation somewhere] dark matter component \citep{Navarro+1995c,NFW96}. In the JAM modelling we use a 10-Gaussian MGE fit to the classical NFW profile
\begin{equation*}
\rho_\text{NFW}(r) \propto 1 / \frac{r}{R_\text{s,NFW}} \left( 1 + \frac{r}{R_\text{s,NFW}} \right)^2.
\end{equation*}
The NFW halo has two free parameters, the scale length $R_\text{s,NFW}$ and a parameter describing the total mass of the halo. We use $v_\text{200}$, which is the circular velocity at the radius $r_\text{200}$ within which the mean density of the halo is 200 times the cosmological [TO DO: how to express this] critical density, i.e.
\begin{eqnarray*}
M_\text{200} &=& M(<r_{200})\\
\frac{M_{200}}{ \frac 43 \pi r_{200}^3} &=& 200 \rho_\text{crit}(z=0) \\
v_\text{200} &=& \sqrt{\frac{GM_{200}}{r_\text{200}}}
\end{eqnarray*}
with $\rho_\text{crit}(z=0)=1.43 \cdot 10^{-7} M_\odot / \text{pc}^3$ in the WMAP5 cosmology by \citet{WMAP5cosm}. How much the mass is concentrated in the center of the NFW halo is given by the concentration of the NFW halo defined by $c_{200}\equiv r_{200} / R_{s,NFW}$. [TO DO: so toll ist das mit der Radiusbenennung noch nicht.????]. There is a close relation between the concentration and halo mass in simulations \citep{NFW96}. \citet{Maccio08} found this relation for the WMAP5 cosmology \citep{WMAP5cosm} to be
\begin{equation}
\langle \log c_{200} \rangle (M_{200}) = 0.830 - 0.098 \log \left(h \frac{M_{200}}{10^{12} M_\odot} \right) \label{eq:Maccio08}
\end{equation}
(their equation 10), with a Gaussian scatter of $\sigma_{\log c_{200}} = 0.105$ (their Table A2).

\paragraph{Modelling.} The full set of fit parameters is $(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta)$ [TO DO: $\beta$ or $\beta_0$???] [TO DO: Einheitlich $\Upsilon_{I,*}$????], where $\beta$ is the constant velocity anisotropy parameter (see Section \ref{sec:model_JAM}). We will investigate this parameter space with a MCMC \citep{emcee} and use priors for the halo parameters to guide the fit to a realistic NFW halo shape.
\\\citet{Dutton10} give a relation for halo vs. stellar mass for late-type galaxies. For an Chabrier IMF stellar population they found
\begin{equation*}
y = y_0 \left( \frac{x}{x_0} \right)^\alpha \left[ \frac 12 + \frac 12 \left(\frac{x}{x_0} \right)^\gamma \right]^{(\beta - \alpha)/\gamma},
\end{equation*}
where $x= m_*$ [$M_\odot h^{-2}$] is the stellar mass, $y = \frac{\langle M_{200}\rangle}{m_*}$ and $\langle M_{200}\rangle$ [$M_\odot h^{-2}$] is the mean halo mass. The parameters for the mean and $2\sigma$ error curves for this relation are$\alpha = -0.5\pm0.15$, $\beta = 0$, $\gamma = 1.0$, $\log_{10} x_0 = 10.4$, $\log_{10} {y_0}_{-0.24}^{+0.28}$ \citet{Dutton10}. Using the stellar mass estimate for J1331 from \citet{SWELLSI} $m_* = (1.06 \pm 0.25) \cdot 10^{11} M_\odot$ for the Chabrier IMF estimate [TO DO: introduce somewhere], we find ${v_{200}} = (202_{-33}^{+44})_{-13}^{+12}$. The first of the two quoted errors is due to the $2\sigma$ scatter in the relation by \citet{Dutton10}. The second error is the propagated error due to the uncertainty in the stellar mass. We use this as a rough estimate for the halo of J1331 and as Gaussian prior on $v_{200}$, 
\begin{equation*}
p(v_{200}) = \mathscr{N}(200 \text{km/s} ,40 \text{km/s}).
\end{equation*}
\\We also use the concentration vs. halo mass relation by \citet{Maccio08} in Equation \ref{eq:Maccio08} as a prior on the concentration, i.e.
\begin{equation*}
p(\log c_{200} \mid v_{200}) = \mathscr{N}\left(\langle \log c_{200} \rangle (M_{200}) \mid 0.105 \right).
\end{equation*}
\\For the velocity anisotropy parameter $\beta$ we will again employ a uniform prior 
\begin{equation*}
p(\beta) = \mathscr{U}(-0.5,+0.5)
\end{equation*}
to exclude very unrealistic anisotropies. The full prior used is then
\begin{eqnarray*}
&&p(\Upsilon_{I,*},R_\text{S,NFW},v_{200},\beta) \\
&&= \frac{1}{\ln\left( 10 R_{s,NFW}\right)} p(\log c_{200} \mid v_{200}) \cdot p(v_{200}) \cdot p(\beta), 
\end{eqnarray*}
where the factor $1/\ln\left( 10 R_{s,NFW}\right)$ is the Jacobian of the transformation from the halo parameters $(v_{200},\log c_{200})$ [TO DO: introduce concentration] to $(v_{200},R_{s,NFW})$.
\\We restrict the $v_\text{rms}$ fit to a region $R' \lesssim 3.5$ arcsec, approximately within the effective half-light radius $R_\text{eff} = 2.6$ arcsec  [TO DO: make sure R' everywhere ???]. We also include the Einstein mass $M(<R_\text{ein}$ with a 10\% error as an additional constraint in the fit. [TO DO: Didn't include the results from the Moster 2010 relation, because they where quite close to the Dutton 2010 relation anyway. Or should I?]

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $R_\text{s,NFW}$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200 \text{km/s},40 \text{km/s})$ (green) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \ref{eq:Maccio08} in terms of $v_{200}$ vs. $R_\text{s,NFW}$ with $1\sigma$ scatter (blue). The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse). The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}. [TO DO: Rename $\beta_0$ to $\beta_z$, rename $R_\text{s,NFW}$ to $r_\text{s,NFW}$, rename $\Upsilon_*$ to $\Upsilon_{I,*}$]}
\label{fig:modelB4_triangle}
\end{figure*}

@@

\begin{figure*}
\centering
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=0.8\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_vcirc.ps}
  \caption{Circular velocity curve.}
  \label{fig:modelB4_vcirc}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:F814WMGE}) and dark matter (grey). [TO DO: Is this really the spherical $r$? I would think it is actually the cylindrical $R$.] \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.[TO DO: radius benennungen sind irgendwie verrutscht]}
\label{fig:modelB4_models}
\end{figure*}

\paragraph{Rotation curve.} Following the procedure in Section \ref{sec:model_JAM} we find the rotation curve from the best fit mean model in Table \ref{tab:modelB4_bestfit} by fitting the rotation parameter $\kappa'$ to the symmetrized $v_\text{rot}$ data within $R' = 3.5$ arcsec. The best fit with $\kappa' = 0.76$ is shown in the second panel of Figure \ref{fig:modelB4_vrot}. The third panel gives the dispersion that was calculated simply by $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. Our assumptions for $\kappa(R)$ nicely reproduce a $v_\text{rot}$ model with counter-rotating core. Although we fitted $v_\text{rot}$ only to the inner regions, the extrapolation to large radii fits the data also very well. While the dispersion $\sigma$ in the center fits by construction quite good, there is a huge discrepancy at large radii. The predicted dispersion is much larger than the data; we would expect the disk rotationally supported and therefore have a low velocity dispersion; especially dispersions as high as $\sim 200 km/s$ are more likely to be observed in the pressure supported bulges of galaxies. There \emph{might} be something unexpeted with the $\sigma$ measurements around $\sim 5$ arcsec, but at large radii the the best fit model NFW halo is simply too massive.

\begin{figure*}
\centering
\includegraphics[width=0.7\linewidth]{fig/B4_rms_rot_curves_best_model.ps}
\caption{Generating the rotation curve from the JAM model with NFW halo and constant velocity anisotropy with the mean parameters in Table \ref{tab:modelB4_bestfit} and with the best fit rotation parameter $\kappa' = 0.76$ in Equation \ref{eq:kappa_profile} (red solid lines). The second velocity moment in the first panel and the first velocity moment in the second panel with the additional fit parameter $\kappa'$ were fitted to the symmetrized data (solid blue points). The velocity dispersion is simply $\sigma = \sqrt{v_\text{rms}^2 - v_\text{rot}^2}$. At larger radii we compare the unsymmetrized data (open blue dots), the gas kinematics from \citet{SWELLSV} (green diamonds) and a JAM model using the same model parameters but the light distribution MGE generated from the Ellipse model in Figure [TO DO: REF FIGURE] as a prediction for the outer regions of J1331 (red dashed lines). The central regions are very well reproduced and we can also greatly predict the rotation curve at larger radii. Only at larger radii the $v_\text{rms}$ and $v_\text{rot}$ overestimate the measurements, probably due to a too massive NFW halo.}
\label{fig:modelB4_vrot}
\end{figure*}

[TO DO: $R_\text{s,NFW}$ is a spherical radius. Should be a small $r_\text{s,NFW}$ everywhere.]
